S. Bikulcius Thesis: Analysis

### 2024-03-14 S. Bikulcius Thesis/analysis_report.Rmd

---
title: 'S. Bikulcius Thesis: Analysis'
author: "Micah E. Hirsch"
date: "2024-03-07"
output: html_document
---

@@

m0 <- glmmTMB(effort_rating ~ 1 + (1|subject) + (1|code), data = accurate_df)
summary(m0)
sjPlot::tab_model(m0, pred.labels = c("Intercept"), dv.labels = "Perceived Listening Effort")
performance::icc(m0)

@@

Quick Note Here: Working Memory was a significant predictor. However, based on the likelihood ratio test, adding it to the model did not significantly improve model fit, which is why on subsequent steps, we are removing it.

@@

m10 <- glmmTMB(effort_rating ~ trial_c + speaker + scale(list_sort_c, scale = F)*speaker + 
                scale(card_sort_c, scale = F)*speaker + (trial_c|subject) + (trial_c|code), data = accurate_df)
summary(m10)
sjPlot::tab_model(m10, pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]", 
                                      "Working Memory", "Cognitive Flexibility", "Working Memory * Speaker [ALS]",
                                      "Cognitive Flexibility * Speaker [ALS]"), 
                  dv.labels = "Perceived Listening Effort")
performance::compare_performance(m8, m10)
performance::test_performance(m8, m10)

@@

m11 <- glmmTMB(effort_rating ~ trial_c + speaker + scale(list_sort_c, scale = F)*speaker + 
                scale(card_sort_c, scale = F)*speaker + scale(pattern_c, scale = F)*speaker + (trial_c|subject) + (trial_c|code), data = accurate_df)
summary(m11)
sjPlot::tab_model(m11, pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]", 
                                      "Working Memory", "Cognitive Flexibility", "Processing Speed",
                                      "Working Memory * Speaker [ALS]",
                                      "Cognitive Flexibility * Speaker [ALS]",
                                      "Processing Speed * Speaker [ALS]"), 
                  dv.labels = "Perceived Listening Effort")
performance::compare_performance(m10, m11)
performance::test_performance(m10, m11)

@@

sjPlot::tab_model(m10, pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]", 
                                      "Working Memory", "Cognitive Flexibility", "Working Memory * Speaker [ALS]",
                                      "Cognitive Flexibility * Speaker [ALS]"), 
                  dv.labels = "Perceived Listening Effort")

@@

>>>>

---
title: 'S. Bikulcius Thesis: Analysis'
author: "Micah E. Hirsch"
date: "2024-03-14"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide

---

@@

m0 <- glmmTMB(effort_rating ~ 1 + (1|subject) + (1|code), data = accurate_df)
sjPlot::tab_model(m0, pred.labels = c("Intercept"), dv.labels = "Perceived Listening Effort")
performance::icc(m0)

@@

Quick Note Here: Working Memory was a significant predictor. However, based on the likelihood ratio test, adding it to the model did not significantly improve model fit, which is why on subsequent steps, we are removing it for now. You'll see that it will eventually get added back in because of the significant interaction between working memory and speaker.

@@

m10 <- glmmTMB(effort_rating ~ trial_c + speaker + scale(list_sort_c, scale = F)*speaker + 
                scale(card_sort_c, scale = F)*speaker + (trial_c|subject) + (trial_c|code), data = accurate_df)
sjPlot::tab_model(m10, pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]", 
                                      "Working Memory", "Cognitive Flexibility", "Working Memory * Speaker [ALS]",
                                      "Cognitive Flexibility * Speaker [ALS]"), 
                  dv.labels = "Perceived Listening Effort")
performance::compare_performance(m8, m10)
performance::test_performance(m8, m10)

@@

m11 <- glmmTMB(effort_rating ~ trial_c + speaker + scale(list_sort_c, scale = F)*speaker + 
                scale(card_sort_c, scale = F)*speaker + scale(pattern_c, scale = F)*speaker + (trial_c|subject) + (trial_c|code), data = accurate_df)
sjPlot::tab_model(m11, pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]", 
                                      "Working Memory", "Cognitive Flexibility", "Processing Speed",
                                      "Working Memory * Speaker [ALS]",
                                      "Cognitive Flexibility * Speaker [ALS]",
                                      "Processing Speed * Speaker [ALS]"), 
                  dv.labels = "Perceived Listening Effort")
performance::compare_performance(m10, m11)
performance::test_performance(m10, m11)

@@

sjPlot::tab_model(m10, pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]", 
                                      "Working Memory", "Cognitive Flexibility", "Working Memory * Speaker [ALS]",
                                      "Cognitive Flexibility * Speaker [ALS]"), 
                  dv.labels = "Perceived Listening Effort",
                  file = "Tables/perceived_effort_model.html")

@@

rm(list = ls())
